Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-30 thesis/thesis.tex
thesis: Add paper as appendix
thesis: Remove extra toc
thesis: Review spelling and grammar

We have applied the our proposed method to clusters with different topologies:

@@

Compared with the mentioned tools, our model can be classified as a non-parameterized model
since it does not depend on parameters referred to the cluster itself
but only hyperparameters such as the initial number of clusters to be found,
or the structure of the Clustering Layer used by DEC model.

Our model is also non-supervised since we do not need to tell the model
which stars belong to the cluster or assit it while its training stage.

@@

From the results shown in Chapter \ref{sec:comparing_and_validating},
we can say that, in general, our model works fine identifying and characterizing open clusters.
So we have succedded building a model non-parameterized and non-supervised for open cluster characterization.
However, some improvements should be done in order to improve its accuracy and precision.

We have built a non-parameterized model since the user does not provide any information
about the cluster profile or its properties.
Although some tweaks can be done regarding the cluster,
like changing the initial number of clusters or modifying the Clustering Layer structure,
in order to improve the final characterization.

@@

Even so, comparing our method with Clusterix,
we can still say that the number of parameters (or hyperparameters) in our model is smaller
and we do not need previous knowledge about the studied cluster.
That makes easier to test different configurations and automate the process.

@@

The first aim after finishing this work is testing the model with a wider range of clusters.
In general we could think of applying it to the whole VizieR catalogue.
That way we could have a better idea about the current limits of our model and we could make adjustments to improve it.
We could determine with better accuracy the topologies that our model works well with,
and which ones the model does not resolve properly.
Even, we could stablish different sets of hyperparameters regarding the topology of the cluster.

With our model, new secondary clusters arise from the data apart of the main ones.
So, it is also interesting the individual study of these new clusters.

@@

At last, we have used the Gaia DR2 database as our data source for this work,
but recently the DR3 dataset has been released.
So it is evident the interest on testing our model with this new data.

@@

\bibliography{references}
\addcontentsline{toc}{chapter}{Bibliography}

\appendix

%\includepdf[pages=-]{anexo.pdf} # TODO: Descomentar cuando el artículo esté hecho
\end{document}

>>>>

We have applied our proposed method to clusters with different topologies:

@@

Compared with the mentioned tools, our model can be cathegorizeed as a non-parameterized
model since it does not depend on parameters referred to the cluster itself
but only hyperparameters such as the initial number of clusters to be found,
or the structure of the Clustering Layer used by DEC model.

Our model is also non-supervised since we do not need to tell the model
which stars belong to the cluster or assist it while its training stage.

@@

From the results shown in Chapter \ref{sec:comparing_and_validating},
we can say that, in general, our model works fine identifying and characterizing open clusters.
So we have succeeded building a model non-parameterized and non-supervised for open cluster characterization.
However, some improvements should be done in order to improve its accuracy and precision.

We have built a non-parameterized model since the user does not provide any information
about the cluster profile or its properties.
Nevertheless some tweaks can be done regarding the cluster,
like changing the initial number of clusters or modifying the clustering layer structure
in order to improve the final characterization.

@@

Despite that, comparing our method with Clusterix,
we can still say that the number of parameters (or hyperparameters) in our model is smaller
and that we do not need previous knowledge about the studied cluster.
That makes easier to test different configurations and automate the process.

@@

The first aim after finishing this work is testing the model with a wider range of clusters.
In general we could think of applying it to the whole VizieR catalogue.
That way we could have a better idea about the current limits of our model and we could make adjustments to improve it.
We could determine with higher accuracy the typologies that our model works well with,
and which ones the model does not resolve properly.
Furthermore, we could stablish different sets of hyperparameters regarding the typology of the cluster.

With our model, new secondary clusters arise from the data apart of the main ones.
Hence, it is also interesting the individual study of these new clusters.

@@

Finally, we have used the Gaia DR2 database as our data source for this work,
but recently the DR3 dataset has been released.
Therefore it is evident the interest on testing our model with this new data.

@@

\bibliography{references}

\includepdf[pages={-},fitpaper]{../paper/paper.pdf}

\end{document}
